EMU Questionnaire - Item & Scale Analysis

### 2024-07-09 02_paper/02_study/02_eye tracking video questionnaire paper/emu_questionnaire.Rmd
X paper

# Read in data
```{r presence_questionnaire, echo=FALSE, results=TRUE}

# # original scale analysis
# 
# # load data files
# quest.data <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
#   dplyr::select(LB01_01:LB01_03,
#                 LM01_01,
#                 LM01_03:LM01_08,
#                 LP01_01:LP01_08,
#                 LV01_01:LV01_03) 
# 
# # descriptive data
# describe(quest.data)
# 
# # omega
# omega(quest.data)
# 
# # creating a matrix
# quest.table <- matrix(data = NA, nrow = 4, ncol = 8)
# rownames(quest.table) <- c("LM", "LB", "LP", "LV")
# colnames(quest.table) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","Alpha")
# 
# # creating a loop
# i <- "LM"
# 
# for (i in c("LM", "LB", "LP", "LV")) {
# 
# loop.data <- quest.data %>%
#   dplyr::select(starts_with(match = i))
# 
# quest.table[i, "N Items"] <- length(loop.data)
# 
# # calculating mean
# loop.data %>%
#   mutate(mean = rowMeans(.)) %>%
#   pull(mean) %>%
#   mean() %>%
#   round(., digits = 2) ->
# quest.table[i, "M"]
# 
# # calculating SD
# loop.data %>%
#   mutate(mean = rowMeans(.)) %>%
#   pull(mean) %>%
#   sd() %>%
#   round(., digits = 2) ->
# quest.table[i, "SD"]
# 
# # calculating Min
# loop.data %>%
#   mutate(mean = rowMeans(.)) %>%
#   pull(mean) %>%
#   min() %>%
#   round(., digits = 2) ->
# quest.table[i, "Min"]
# 
# # calculating Max
# loop.data %>%
#   mutate(mean = rowMeans(.)) %>%
#   pull(mean) %>%
#   max() %>%
#   round(., digits = 2) ->
# quest.table[i, "Max"]
# 
# # calculating Skewness
# loop.data %>%
#   mutate(mean = rowMeans(.)) %>%
#   pull(mean) %>%
#   skewness() %>%
#   round(., digits = 2) ->
# quest.table[i, "Skewness"]
# 
# # calculating Kurtosis
# loop.data %>%
#   mutate(mean = rowMeans(.)) %>%
#   pull(mean) %>%
#   kurtosis() %>%
#   round(., digits = 2) ->
# quest.table[i, "Kurtosis"]
# 
# # calculating Alpha
# alpha <- loop.data %>%
#   cronbach.alpha()
# 
# quest.table[i, "Alpha"] <- round(alpha$alpha,2)
# 
# }
# 
# # rename columns
# rownames(quest.table) <- c("Classroom Management", "Balance", "Presence", "Natural Behavior")
# 
# # format and insert table in manuscript
# papaja::apa_table(
# quest.table,
#   caption = "Scale analysis for teachers' self-assessment",
#   # note = "Write Note here",
#   escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
#   placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
#   font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
# )

# load data files with modified sclaes
quest.data <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
  dplyr::select(LB01_01:LB01_03,
                LM01_01:LM01_08,
                LP01_01:LP01_08,
                LV01_01:LV01_03) %>% 
  rename(
    LZ01_06 = LM01_06,
    LZ01_07 = LM01_07,
    LZ01_08 = LM01_08
    )
```

# Scale analysis 
```{r presence_questionnaire, echo=FALSE, results=TRUE}
# descriptive data
describe(quest.data)

# creating a matrix
quest.table <- matrix(data = NA, nrow = 5, ncol = 8)
rownames(quest.table) <- c("LM", "LB", "LP", "LV", "LZ")
colnames(quest.table) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","Alpha")

@@

for (i in c("LM", "LB", "LP", "LV", "LZ")) {

loop.data <- quest.data %>%
  dplyr::select(starts_with(match = i))

quest.table[i, "N Items"] <- length(loop.data)

# calculating mean
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  mean() %>%
  round(., digits = 2) ->
quest.table[i, "M"]

# calculating SD
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  sd() %>%
  round(., digits = 2) ->
quest.table[i, "SD"]

# calculating Min
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  min() %>%
  round(., digits = 2) ->
quest.table[i, "Min"]

# calculating Max
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  max() %>%
  round(., digits = 2) ->
quest.table[i, "Max"]

# calculating Skewness
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  skewness() %>%
  round(., digits = 2) ->
quest.table[i, "Skewness"]

# calculating Kurtosis
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  kurtosis() %>%
  round(., digits = 2) ->
quest.table[i, "Kurtosis"]

@@

quest.table[i, "Alpha"] <- round(alpha$alpha,2)

# calculating Alpha
omega <- loop.data %>% 
  omega()

@@

# rename columns
rownames(quest.table) <- c("Classroom Management", "Balance", "Presence", "Natural Behavior", "Additional")

# format and insert table in manuscript
knitr::kable(
quest.table,
  caption = "Scale analysis for teachers' self-assessment",
  # note = "Write Note here",
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
)

```
# Item analysis 
```{r item_analysis_classroom_management, echo=FALSE, results='asis'}
quest.data %>%
  dplyr::select(contains("LM")) %>%
  as.data.frame() %>%
  tab_itemscale(CSS = list(
    css.firsttablerow.col7 = "'cronbachs alpha';"
  ))
```

@@

quest.data[, !names(quest.data) %in% c("LZ01_06")] -> clean.data.quest
KMO(clean.data.quest)

@@

ev <- eigen(cor(clean.data.quest))
ap <- parallel(subject = nrow(clean.data.quest),
               var = ncol(clean.data.quest),
               rep = 100,
               cent = .05)
nS <- nScree(x = ev$values,
             aparallel = ap$eigen$qevpea)
plotnScree(nS)

@@

fit2 <- fa(r = clean.data.quest, 
           nfactors = 4, 
           rotate = "varimax")

@@

## Hauptkomponentenanalyse
# 4 Faktoren
# Varimax-Rotation

fit3 <- principal(r = clean.data.quest,
                  nfactors = 3, 
                  rotate = "varimax")

@@

fit3

>>>>

# Scale analysis --> Classroom Management with 16 Items 
```{r presence_questionnaire, echo=FALSE, results=TRUE}

# load data files with modified scales
quest.data1 <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
  dplyr::select(LM01_01:LM01_08,
                LP01_01:LP01_08) %>% 
  rename(LM09 = LP01_01,
         LM10 = LP01_02,
         LM11 = LP01_03,
         LM12 = LP01_04,
         LM13 = LP01_05,
         LM14 = LP01_06,
         LM15 = LP01_07,
         LM16 = LP01_08)

# creating a matrix
quest.table1 <- matrix(data = NA, nrow = 1, ncol = 8)
rownames(quest.table1) <- c("LM")
colnames(quest.table1) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","Alpha")

@@

for (i in c("LM")) {

loop.data <- quest.data1 %>%
  dplyr::select(starts_with(match = i))

quest.table1[i, "N Items"] <- length(loop.data)

# calculating mean
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  mean() %>%
  round(., digits = 2) ->
quest.table1[i, "M"]

# calculating SD
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  sd() %>%
  round(., digits = 2) ->
quest.table1[i, "SD"]

# calculating Min
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  min() %>%
  round(., digits = 2) ->
quest.table1[i, "Min"]

# calculating Max
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  max() %>%
  round(., digits = 2) ->
quest.table1[i, "Max"]

# calculating Skewness
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  skewness() %>%
  round(., digits = 2) ->
quest.table1[i, "Skewness"]

# calculating Kurtosis
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  kurtosis() %>%
  round(., digits = 2) ->
quest.table1[i, "Kurtosis"]

@@

quest.table1[i, "Alpha"] <- round(alpha$alpha,2)

# # calculating Alpha
# omega <- loop.data %>% 
#   omega()

@@

# rename columns
rownames(quest.table1) <- c("Classroom Management")

# format and insert table in manuscript
knitr::kable(
quest.table1,
  caption = "Scale analysis for teachers' self-assessment",
  # note = "Write Note here",
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
)

quest.data1 %>%
  dplyr::select(contains("LM")) %>%
  as.data.frame() %>%
  tab_itemscale(CSS = list(
    css.firsttablerow.col7 = "'cronbachs alpha';"
  ))
```

# # Scale analysis --> Classroom Management (8 Items) and Presence (8 Items) 
```{r presence_questionnaire, echo=FALSE, results=TRUE}

# load data files with modified scales
quest.data2 <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
  dplyr::select(LM01_01:LM01_08,
                LP01_01:LP01_08)

# creating a matrix
quest.table2 <- matrix(data = NA, nrow = 2, ncol = 8)
rownames(quest.table2) <- c("LM", "LP")
colnames(quest.table2) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","Alpha")

for (i in c("LM")) {

loop.data <- quest.data2 %>%
  dplyr::select(starts_with(match = i))

quest.table2[i, "N Items"] <- length(loop.data)

# calculating mean
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  mean() %>%
  round(., digits = 2) ->
quest.table2[i, "M"]

# calculating SD
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  sd() %>%
  round(., digits = 2) ->
quest.table2[i, "SD"]

# calculating Min
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  min() %>%
  round(., digits = 2) ->
quest.table2[i, "Min"]

# calculating Max
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  max() %>%
  round(., digits = 2) ->
quest.table2[i, "Max"]

# calculating Skewness
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  skewness() %>%
  round(., digits = 2) ->
quest.table2[i, "Skewness"]

# calculating Kurtosis
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  kurtosis() %>%
  round(., digits = 2) ->
quest.table2[i, "Kurtosis"]

quest.table2[i, "Alpha"] <- round(alpha$alpha,2)

# rename columns
rownames(quest.table2) <- c("Classroom Management", "Presence")

# format and insert table in manuscript
knitr::kable(
quest.table2,
  caption = "Scale analysis for teachers' self-assessment",
  # note = "Write Note here",
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
)

quest.data2 %>%
  dplyr::select(contains("LM")) %>%
  as.data.frame() %>%
  tab_itemscale(CSS = list(
    css.firsttablerow.col7 = "'cronbachs alpha';"
  ))

quest.data2 %>%
  dplyr::select(contains("LP")) %>%
  as.data.frame() %>%
  tab_itemscale()

@@

# quest.data[, !names(quest.data) %in% c("LZ01_06")] -> clean.data.quest
# KMO(clean.data.quest)

@@

ev <- eigen(cor(quest.data))
ap <- parallel(subject = nrow(quest.data),
               var = ncol(quest.data),
               rep = 100,
               cent = .05)
nS <- nScree(x = ev$values,
             aparallel = ap$eigen$qevpea)
plotnScree(nS)

@@

fit2 <- fa(r = clean.data.quest, 
           nfactors = 4, 
           rotate = "varimax",
           cutoff = .3)

@@

## Hauptkomponentenanalyse
# 2 Faktoren
# Varimax-Rotation

fit3 <- principal(r = quest.data,
                  nfactors = 2, 
                  rotate = "varimax")

@@

print(loadings(fit3), cutoff= .3)
